---
title: "Practice_6.2"
output: html_document
date: "2023-10-29"
---

I guess you kept the code to be fixed below. As there arr no instructions in the .Rmd, I still tried to run it in case you did some changes. The code below does not work. In order to generate HTML, you have to deactivate code chunk using  'eval=F' 


```{r echo=FALSE, eval=F, purl=F}
grow<-function(start_1,start_2){
  num_gen<-30
  N1 <- rep(0,10)
  N2 <- rep(0,10)
  generation<-rep(1,num_gen)
  growth.rate<-1.2
  K1<-100
  K2<-120
  a12<-0.8
  a21<-0.8
  N1[1]<-0
  N2[1]<-start_2
  for (i in 2:3)  {
    N1[i] = N1[i-1] + (3.2* N1[i-1] * ((K1-N1[i-1]-(a12*N2[i-1]))/K1))
    N2[i] = N2[i] + (growth.rate * N2[i-1] * ((K2-N2[i-1]-(a21*N1[i-1]))*K2))
    generation[1]=1
    print (N1[i])
  }
  if (N1[1]>2){
    plot(N1~generation,typ="b",ylim=c(0,min(c(K1,K2))),ylab="N")
  }  else {
    plot(N1~generation,typ="n",ylim=c(0,min(c(K1,K2))),ylab="N")
  }
  print(N2[1])
  if (N2[1]>0){
    lines(N2~generation,typ="b",col=2)}
  par(mar=c(9,4,1,1),mfrow=c(5,1),las=1)
 
   }



grow(1,0)
text(4,110,"Species 1 alone")

grow(0,1)
text(4,110,"Species 2 alone")

grow(1,2)
text(6,110,"Both Species competing")

```

The code below is working. I guess this is your solution. I added the packages library at the beginning as your code is not stand-alone without it:

```{r echo=FALSE, purl=F}
library (animation)

grow <- function(start_1, start_2) {
  num_gen <- 30
  N1 <- rep(0, num_gen)
  N2 <- rep(0, num_gen)
  generation <- 1:num_gen
  growth.rate <- 1.2
  K1 <- 100
  K2 <- 120
  a12 <- 0.8
  a21 <- 0.8
  N1[1] <- start_1
  N2[1] <- start_2
  
  for (i in 2:num_gen) {
    N1[i] <- N1[i - 1] + (1.2 * N1[i - 1] * (1 - N1[i - 1] / K1 - a12 * N2[i - 1] / K1))
    N2[i] <- N2[i - 1] + (1.2 * N2[i - 1] * (1 - N2[i - 1] / K2 - a21 * N1[i - 1] / K2))
  }
  
  par(mfrow = c(3, 1), mar = c(2, 4, 2, 2))  # 調整邊距的大小
  plot(generation, N1, type = "b", ylim =c(0, 120), main = "Population Dynamics")
  lines(generation, N2, col = 2, type = "b")
  
  if (start_1 > 0 & start_2 == 0) {
    text(10, 100, "Species 1 alone")
  } else if (start_1 == 0 & start_2 > 0) {
    text(10, 100, "Species 2 alone")
  } else {
    text(10, 100, "Both Species competing")
  }
}

saveGIF({
grow(1, 0)
grow(0, 1)
grow(1, 2)
})

```

You need to close code chunk
